Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
fix digits and round
reflow
mention aggregated windows
fix count percent

options(digits = 3)

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
count <- readRDS('../data/derived-data/02-landcover-scale-count.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
timedefs[, c('mindate', 'maxdate') := .(as.IDate(mindate), as.IDate(maxdate))]
```

@@

An illustrative multilayer network was generated, informed by previous social, 
spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
distance threshold was 50 m. The spatial resolution of the land cover 
raster was 30 m. -->Relocations were predominantly in open 
(`r count[res == 30 & lc == 1, percent]`%) and forest 
(`r count[res == 30 & lc == 2, percent]`%) habitats 
compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
Despite this, individuals were more strongly connected in foraging and open 
habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
forest: 0.11, open: 0.23). There was a seasonal difference in association, 
individuals were more connected between approximately October - June 
(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
than between approximately June - October 
(mean graph strength in time windows; 1: 0.04, 3: 0.03).

>>>>

options(digits = 2, round = 2)

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
count <- readRDS('../data/derived-data/02-landcover-scale-count.Rds')
count[lc %in% c(1, 2, 3), percent := N / sum(N) * 100, by = res]
timedefs <- fread('../data/supp-data/timecut-defs.csv')
timedefs[, c('mindate', 'maxdate') := .(as.IDate(mindate), as.IDate(maxdate))]
```

@@

An illustrative multilayer network was generated, informed by previous social, 
spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
distance threshold was 50 m. The spatial resolution of the land cover 
raster was 30 m. -->Relocations were predominantly in open 
(`r count[res == 30 & lc == 1, percent]`%) and forest 
(`r count[res == 30 & lc == 2, percent]`%) habitats 
compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
Despite this, individuals were more strongly connected in foraging and open 
habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
forest: 0.11, open: 0.23). There was a seasonal difference in association, 
individuals were more connected between approximately October - June 
(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
than between approximately June - October 
(mean graph strength in time windows; 1: 0.04, 3: 0.03). The time windows
were aggregated from the finer scale time windows presented above (time window 1:
2-5, time window 2: 6-11, time window 3: 12-15, time window 4: 16-20).
